### 2016-11-19 R/ITHIM.Rmd
Tweaked figures for Jonathan's talk

## ITHIM.NY <- ITHIMList[["NY"]]
## ITHIM.NY <- updateITHIM(ITHIM.NY, parName = "muNonTravel", 10)
## foo2 <- compareModels(ITHIM.national,ITHIM.NY)
## foobar2 <- data.frame(cbind(melt(foo2$daly.delta),paste0("ageClass",1:8)),State = "NY")
## foobar <- rbind(foobar1,foobar2)
## names(foobar) <- c("delta.DALY","Sex","Disease","ageClass","State")

foobar <- within(foobar, {
  Disease[Disease == "BreastCancer"] <- "Breast Cancer"
  Disease[Disease == "ColonCancer"] <- "Colon Cancer"
  Disease <- factor(Disease, levels = c("Breast Cancer", "Colon Cancer", "Dementia", "Depression", "Diabetes"))
})

p <- ggplot( subset(foobar,ageClass != "ageClass1"), aes(ageClass,-delta.DALY/1e3, fill = Sex) )

p + geom_bar(stat="identity", position = "dodge") +
theme(axis.title=element_blank()) +
facet_grid( Disease ~ ., scales = "free") +
scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") +
scale_x_discrete(name="", labels = c("5-14","15-29","30-44","45-59","60-69","70-79","80+"))

@@

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(37.5, 120, length.out = 10)
muNonTravelVec <- c(1, 10, 25)
DTotal <- data.frame()

@@

p <- ggplot(subset(D, disease %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes", "CVD") & type == "daly"), aes(x = ageClass, y = burden/1e3, fill = sex)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + scale_x_discrete(name="", labels = c("0-4","5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="Nationwide Burden (thousands)") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8)) + facet_grid( . ~ disease, scales = "free_y")
```

>>>>

ITHIM.NY <- ITHIMList[["NY"]]
ITHIM.NY <- updateITHIM(ITHIM.NY, parName = "muNonTravel", 10)
foo2 <- compareModels(ITHIM.national,ITHIM.NY)
foobar2 <- data.frame(cbind(melt(foo2$daly.delta),paste0("ageClass",1:8)),State = "NY")
foobar <- rbind(foobar1,foobar2)
names(foobar) <- c("delta.DALY","Sex","Disease","ageClass","State")

foobar <- within(foobar, {
  Disease[Disease == "BreastCancer"] <- "Breast Cancer"
  Disease[Disease == "ColonCancer"] <- "Colon Cancer"
  Disease <- factor(Disease, levels = c("Breast Cancer", "Colon Cancer", "Dementia", "Depression", "Diabetes", "CVD"))
})

p <- ggplot( subset(foobar,ageClass != "ageClass1"), aes(ageClass,-delta.DALY/1e3, fill = State))

p + geom_bar(stat="identity", position = "dodge") +
theme(axis.title=element_blank()) +
facet_grid( Disease ~ Sex, scales = "free" ) +
scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") +
scale_x_discrete(name="", labels = c("5-14","15-29","30-44","45-59","60-69","70-79","80+"))

@@

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(45, 120, length.out = 10)
muNonTravelVec <- c(1, 10, 25)
DTotal <- data.frame()

@@

p <- ggplot(subset(D, disease %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes", "CVD") & type == "daly"), aes(x = ageClass, y = burden/1e3, fill = sex)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + scale_x_discrete(name="", labels = c("0-4","5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="DALYs Nationwide (thousands)") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8)) + facet_grid( . ~ disease, scales = "free_y")
```
